\documentclass[a4paper,10pt,fleqn]{article}

%%% Packages
\usepackage{graphicx} % use graphics
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{multicol}
\usepackage{placeins} % \FloatBarrier (sudo apt install texlive-latex-extra)
\usepackage[bottom]{footmisc} % avoid images below footnotes
\usepackage[utf8]{inputenc}
%\usepackage[danish]{babel}
\usepackage[T1]{fontenc}
\usepackage{ctable} % for \specialrule command
\usepackage{caption} % for setting caption width

%\usepackage{algorithm}
%\usepackage{algorithmic}

%%% Modify page layout
\setlength{\textwidth}{160 mm} % line width
\setlength{\oddsidemargin}{0 mm}  % left margin
\setlength{\topmargin}{-1.5 cm} % top margin
\setlength{\textheight}{25.0 cm} % page width
%\pagestyle{empty} % remove page numbers
\setlength{\parindent}{0 mm} % indent at the beginning of a paragraph
\setlength{\parskip}{2 mm} % vertical distance between paragraphs

% fancy header
\usepackage{fancyhdr}
\newcommand{\CourseNumber}{SDU UAS Center}%
\newcommand{\CourseTitle}{Introduction to UAS Techology (RMUAST Spring 2019)}%
\newcommand{\Author}{Frederik Mazur Andersen}%
\pagestyle{fancy}
\lhead{\bfseries \CourseNumber} 
\chead{} 
\rhead{\bfseries \CourseTitle} 
\lfoot{} 
\cfoot{} 
\rfoot{Page \thepage} 

%\renewcommand{\footnotesize}{\scriptsize}

% Text fonts
\usepackage{palatino}

\usepackage[hyperindex=true,pdftitle={},pdfauthor={},colorlinks=true,
pagebackref=false,citecolor=blue,linkcolor=blue, urlcolor=blue, plainpages=false,
%pagebackref=false,citecolor=black,linkcolor=black, urlcolor=black, plainpages=false,
pdfpagelabels]{hyperref} % colourlinks=false for printing

\usepackage[round,colon,authoryear]{natbib}
\usepackage[htt]{hyphenat}

\begin{document}

\vspace*{5mm}

\LARGE
\begin{center}Flash firmware on telemetry modules

\normalsize
\vspace{2mm}
Frederik Mazur Andersen \href{mailto:fm@mmmi.sdu.dk}{fm@mmmi.sdu.dk}

\vspace {3mm}
\end{center}

\normalsize
\vspace{5mm}
\FloatBarrier


\section{Flash telemetry modules}
In order to show the current telemetry and not the average rssi a change has been made in the firmware of the radio modules. To flash your telemetry modules with the new firmware following the steps below.

\begin{enumerate}
\item Download and extract the zip file from blackboard.
\item Go into the downloaded folder in terminal
\item Make sure only one telemetry module is connected though usb. (Should be port ttyUSB0)
\item install pexpect with: \texttt{pip install pexpect} If running Ubuntu 16.04 you might have to run \texttt{pip install --upgrade pexpect} to get the latest version.\footnote{Ensure it gets installed for Python 2.7. You might have to use \texttt{pip2} instead.} 
% Need to use -{}- to stop latex making -- into a single line. 
\item Run command: \texttt{python sik\_uploader.py -{}-port /dev/ttyUSB0 -{}-baudrate 57600 radio\_hm\_trp\_2.0\_current\_rssi.ihx}
\item Repeat for second module. Both modules needs to be flashed. 
\item Setup both modules though apm-planner again as instructed in the weekly notes. 
\end{enumerate}


%\bibliographystyle{plainnat}
%\bibliography{kj_nourls} 

\end{document}


